Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/workload.tex
shrink table
table

\begin{table}
\center
\begin{tabular}{ |l|l|r|c|c|c| }
\hline
$M$ & margin & $n$ & Prov & SO & EoR \\
\hline
0.1&0.25&25&0.221&0.152&0.115\\
&0.2&41&0.178&0.169&0.105\\
&0.15&73&0.202&0.186&0.141\\
&0.1&163&0.222&0.182&0.107\\
&0.05&657&0.227&0.192&0.127\\
&0.04&1027&0.237&0.193&0.124\\
&0.03&1825&0.246&0.194&0.124\\
&0.02&4105&0.246&0.195&0.124\\
&0.01&16423&0.246&0.196&0.124\\
\hline
0.01&0.25&85&0.792&0.707&0.559\\
&0.2&133&0.826&0.71&0.593\\
&0.15&239&0.817&0.712&0.549\\
&0.1&539&0.805&0.717&0.567\\
&0.05&2163&0.817&0.721&0.569\\
&0.04&3381&0.82&0.722&0.563\\
&0.03&6011&0.824&0.723&0.573\\
&0.02&13527&0.824&0.723&0.57\\
&0.01&54117&0.824&0.724&0.57\\
\hline
0.001&0.25&149&0.962&0.889&0.783\\
&0.2&235&0.963&0.89&0.768\\
&0.15&421&0.958&0.894&0.801\\
&0.1&951&0.958&0.894&0.793\\
&0.05&3815&0.96&0.896&0.785\\
&0.04&5965&0.961&0.896&0.791\\
&0.03&10607&0.961&0.897&0.787\\
&0.02&23869&0.962&0.897&0.787\\
&0.01&95491&0.962&0.897&0.787\\
\hline
\end{tabular}
\caption{For various margins, this table gives the minimum first round size $n$ to achieve at most a probability $M$ of a \emph{misleading sample} in the first round. The corresponding stopping probabilities of \Providence, SO \BRAVO, and EoR \BRAVO are given for each value of $n$.}
\label{tab:misleading}
\end{table}

\textbf{Misleading SO \BRAVO sequences.} As we consider the idea of misleading samples, it is noteworthy that SO \BRAVO suffers from a different and unique type of misleading result.

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{so_misleading.png}
\caption{The total number of ballots sampled on average in our simulations for various round schedules parameterized by $p$ the conditional stopping probability used to select each round size.}
\label{fig:misleading_2}
\end{figure}

>>>>

\subsubsection{Misleading SO \BRAVO sequences.} As we consider the idea of misleading samples, it is noteworthy that SO \BRAVO suffers from a different and unique type of misleading result.

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{so_misleading.png}
\caption{The proportion of sequences that are misleading sequences in the SO \BRAVO audit as a function of $p$.}
\label{so_misleading}
\end{figure}
